Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2014-11-24 AO_bondedSi.tex
add water mark to the draft for pre-publication circulation
Add 60 nm curve to the existing figure 4, closes #1

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/20140421_absoluteB.pdf}}
\caption{Modeled etalon transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 35 nm (cyan triple-dot dashed curve)\label{figEtalonRelTrans}.  The curves are examples from a family defined in Equation \ref{eqFP}.   The limit of no gap is 100\% transmissive, compared to a DSP reference.  A 35 nm gap degrades the transmission over a DSP reference by 4\% at 1200 nm.}
\end{figure}

>>>>

%\usepackage{draftwatermark}
%\SetWatermarkText{DRAFT}
%\SetWatermarkScale{6}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/Rel_etalon_trans_0-60nm.pdf}}
\caption{Modeled etalon transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 60 nm (cyan triple-dot dashed curve)\label{figEtalonRelTrans}.  The curves are examples from a family defined in Equation \ref{eqFP}.   The limit of no gap is 100\% transmissive, compared to a DSP reference.  A 60 nm gap degrades the transmission over a DSP reference by 12\% at 1200 nm.}
\end{figure}
